Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-09-07 texor.Rmd
try to commit rendered output from GitHub action
do git add before commit
fix some typos

As a consequence of this project, the journal web site has been furnished with an additional link titled "CONTRIBUTE". Visiting this link will give you details on how to report a problem with an article that you are readin, or even to make a suggestion on improving operations.

@@

One of the useful elements when an article is in HTML format is that figures can be made richer with an `alt-text` element. In an R Markdown code chunk generating a figure, this can be set using `fig.alt`. Alternative text provides a textual alternative to non-text content in HTML documents, serves various purposes: read by screen readers are accessible to people with visual disabilities, is displayed in place of the image if it fails to load, and can serve to assist search engines. It is a work in progress to have these added by authors of new article submissions, and at some potin would be useful to add to the converted legacy articles.

>>>>

As a consequence of this project, the journal web site has been furnished with an additional link titled "CONTRIBUTE". Visiting this link will give you details on how to report a problem with an article that you are reading, or even to make a suggestion on improving operations.

@@

One of the useful elements when an article is in HTML format is that figures can be made richer with an `alt-text` element. In an R Markdown code chunk generating a figure, this can be set using `fig.alt`. Alternative text provides a textual alternative to non-text content in HTML documents, serves various purposes: read by screen readers are accessible to people with visual disabilities, is displayed in place of the image if it fails to load, and can serve to assist search engines. It is a work in progress to have these added by authors of new article submissions, and at some point would be useful to add to the converted legacy articles.
